Using reference models in variable selection \vspace{.1in}

### 2020-02-08 paper/ref_approach.tex
added one sd error bar in figure caption

% TODO: Bigger and more distinctive symbols in figures
% label order: steplm, bayes.step, projpred
\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/rmse_vs_fdr_parallel.pdf}
  \caption{Root mean square error (RMSE) against false discovery rate in the minimal subset variable selection.}
  \label{fig:rmse_vs_fdr}
\end{figure}

@@

In the experiments shown in the next sections, we include an additional iterative
method which we refer to as 'iterative lasso'. It consists of the same iterative
algorithm as iterative projpred expect for not using any reference model but
the lasso method for variable selection, instead.
That is, it uses the observed target values instead of predictions of the reference model.
Iterative lasso can help to distangle the effects
of the iterative procedure and the usage of a reference model in complete feature selection.

@@

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/sensitivity_vs_fdr_iterated.pdf}
  \caption{Sensitivity against false discovery rate based on 100 data simulations.\\}
  \label{fig:sensitivity_vs_fdr_iterated}
\end{figure}

@@

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_sensitivity_vs_fdr.pdf}
  \caption{Sensitivity against false discovery rate based on 100 bootstrap samples.\\}
  \label{fig:bodyfat_sensitivity_vs_fdr}
\end{figure}

>>>>

% TODO: Bigger and more distinctive symbols in figures
% label order: steplm, bayes.step, projpred
\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/rmse_vs_fdr_parallel.pdf}
  \caption{Root mean square error (RMSE) against false discovery rate in the minimal subset variable selection with one standard deviation error bars.}
  \label{fig:rmse_vs_fdr}
\end{figure}

@@

In the experiments shown in the next sections, we include an additional iterative
method which we refer to as `iterative lasso'. It consists of the same iterative
algorithm as iterative projpred expect for not using any reference model but
the lasso method for variable selection, instead.
That is, it uses the observed target values instead of predictions of the reference model.
Iterative lasso can help to distangle the effects
of the iterative procedure and the usage of a reference model in complete feature selection.

@@

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/sensitivity_vs_fdr_iterated.pdf}
  \caption{Sensitivity against false discovery rate based on 100 data simulations with one standard deviation error bars.\\}
  \label{fig:sensitivity_vs_fdr_iterated}
\end{figure}

@@

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_sensitivity_vs_fdr.pdf}
  \caption{Sensitivity against false discovery rate based on 100 bootstrap samples with one standard deviation error bars.\\}
  \label{fig:bodyfat_sensitivity_vs_fdr}
\end{figure}
